Blog post: Identifying and manipulating non-breaking spaces

### 2020-02-29 text/20/non-breaking-space.Rmd
More minor fixes to blog files

![Figure 1. Screenshot of a file inside Notepad](non-breaking-space01.png)

@@

![Figure 2. Screenshot of a file inside RStudio](non-breaking-space02.png)

>>>>

![Figure 1. Screenshot of a file inside Notepad](http://www.pmean.com/images/20/non-breaking-space01.png)

@@

![Figure 2. Screenshot of a file inside RStudio](http://www.pmean.com/images/20/non-breaking-space02.png)
